Process Genotypes For Ancestry Analysis

### 2019-09-19 code/Ancestry_PCA.Rmd
Ancestry Chunk1v1

#i=22
for i in {1..22}
do
	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

@@

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf

done

#Merge All Plink Files into genome wide
for i in {2..22}
do
  echo 1000Genomes_chr$i >> Merge.List
done

plink --bfile 1000Genomes_chr1 --merge-list Merge.List --make-bed --out 1000Genomes_Merged
rm 1000Genomes_chr*

>>>>

#Make Plink IDV List of all 1000G Ref Samps to pull
cat CEU.samples.list YRI.samples.list CHB.samples.list JPT.samples.list > 1000G_IDV.list
paste 1000G_IDV.list 1000G_IDV.list > foo.txt
mv foo.txt 1000G_IDV.list

#Pull 1000G Data, convert to plink, Filt for INDV and SNPs
for i in {1..22}
do
	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

@@

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf
done

#Merge All Plink Chr Files 
for i in {2..22}
do
  echo 1000Genomes_chr$i >> Merge.list
done

plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged

rm 1000Genomes_chr*
rm *.list
```
